---
title: "Modeling the Contribution of Offshore Wind to the Grid Mix and Air Quality Implications:\nNational Approach Results and Analysis"
author: "Morgan Browning"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    number_sections: yes
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

***

# Disclosure

This document functions as an all-inclusive working directory for synthesis and graphical analysis of the results from the offshore wind research of Morgan Browning, an ORISE Fellow at the U.S. Environmental Protection Agency's Office of Research and Development. This document and its contents are not finalized nor are intended for publication. 

It is annotated primarily for ease of reproducability and a general understanding of the results. 

# Setup

Three scripts are loaded into this markdown document to allow for analysis of the data. The setup script loads the library, creates generalized functions, and creates global variables for color scales and factors. The data script loads an excel spreadsheet with all of the results data and performs the majority of data munging. The results script creates charts, graphs, and tables. This report functions as the annotated synthesis of the data and results.

Graphs are provided with many variations to meet criteria of different publication and presentation platforms. Formats may be chosen using the `colorcalls` toggles

```{r setup, include = FALSE}
# Sets global knit options and loads the setup and data import scripts for the project. Code is hidden for ease of reading. Was running into issues when cacheing results, so have set cache to false. Time to knit <5 minutes, so it does not cause much of an issue. Will consider cacheing in the future if the issue is resolved.
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE, tidy = TRUE, cache = FALSE)
```
```{r, include = FALSE}
source("osw_Scripts/osw_setup.R")
```
```{r, include = FALSE}
source("osw_Scripts/osw_data.R")
```
```{r, include = FALSE}
source("osw_Scripts/osw_results.R")
```
```{r colorcalls}
# Creates toggles for selecting the color scale of graphics to be printed [color, black & white, gray]. More than one may be selected.
color <- 1
bw <- 0
gray <- 0
```

# Scenarios

The nested parametric sensitivity analysis was built on combinations of two sets of scenarios:

1. Electric sector CO~2~ emissions caps, as a linear decrease to a given % decrease from 2010 emissions by 2050  
  + Business and usual emissions represent approximately a 20% reduction in CO~2~ emissions

2. Cost reductions of offshore wind, as a linear decrease to a given % decrease from 2010 costs by 2035, then level costs to 2050  
  + A 20% cost reduction is used as the base case, assuming very conservative technological advancement and little benefit of economies of scale
  + Cost curves are set to resolve by 2035 as estimated based on NREL LCOE cost projections for offshore wind

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) emissionsscen_col
if(color > 0) costscen_col
```

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) emissionsscen_bw
if(bw > 0) costscen_bw
```

# LCOE

EIA's AEO 2019 provides the following values for the estimated levelized cost of electricity (capacity-weighted average) for new generation resources entering service in 2023 (2018 $/MWh). Offshore wind has the highest total LCOE by a large margin. The second most expensive technology is biomass. The AEO LCOE was used in the calculation of offshore wind costs for the above cost curves, but LCOE is not directly used in the model.

```{r}
lcoe_table
```

# Offshore Wind

As offshore wind is the primary technology being assessed in this research, we have explored many facets of offshore wind buildout. These facets are explored below, both at a regional and national cumulative level.

## Capacity Buildout

Cumulative and new addition offshore wind capacity across all nine census regions, by cost and emissions reduction scenario.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cap_col_side
if(color > 0) newcap_col_top
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cap_bw_side
if(bw > 0) newcap_bw_top
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(gray > 0) cap_gray_side
if(gray > 0) newcap_gray_top
```

## Total Capacity

Total offshore wind capacity across all nine census regions in 2050, by cost and emissions reduction scenario.

```{r}
if(color > 0) cap_col_heat 
if(bw > 0) cap_bw_heat
```
```{r}
cap_2050_table
```

## Output

Total offshore wind electricity output across all nine census regions, by cost and emissions reduction scenario. Results show almost identical trajectories for total capacity and output due to the non-dispatchable quality of offshore wind. All generated electricity is utilized in the modeled scenarios.

```{r}
if(color > 0) output_col_side
if(bw > 0) output_bw_side
if(gray > 0) output_gray_side
```
```{r}
output_2050_table 
```

## Regions

Cumulative and new addition offshore wind capacity by region. Regions are listed from least to highest electricity output.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cap_reg7_col
if(color > 0) newcap_reg7_col
if(color > 0) cap_reg1_col
if(color > 0) newcap_reg1_col
if(color > 0) cap_reg2_col
if(color > 0) newcap_reg2_col
if(color > 0) cap_reg3_col
if(color > 0) newcap_reg3_col
if(color > 0) cap_reg9_col
if(color > 0) newcap_reg9_col
if(color > 0) cap_reg5_col
if(color > 0) newcap_reg5_col
```

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cap_reg7_bw
if(bw > 0) newcap_reg7_bw
if(bw > 0) cap_reg1_bw
if(bw > 0) newcap_reg1_bw
if(bw > 0) cap_reg2_bw
if(bw > 0) newcap_reg2_bw
if(bw > 0) cap_reg3_bw
if(bw > 0) newcap_reg3_bw
if(bw > 0) cap_reg9_bw
if(bw > 0) newcap_reg9_bw
if(bw > 0) cap_reg5_bw
if(bw > 0) newcap_reg5_bw
```

Cumulative and new addition offshore wind capacity by region, emissions reduction, and cost reduction.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cap_allreg_col
if(color > 0) newcap_allreg_col
if(color > 0) cap_allreg_col_free
if(color > 0) newcap_allreg_col_free
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cap_allreg_bw
if(bw > 0) newcap_allreg_bw
if(bw > 0) cap_allreg_bw_free
if(bw > 0) newcap_allreg_bw_free
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
cap_region_table
output_region_table
```

Map of average total capacity 

```{r}
if(color > 0) regOSW_map_col
if(bw > 0) regOSW_map_bw
```

# Grid Mix

## Baseline Production

Grid mix without any offshore wind cost reduction or emissions cap.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) baseprod_line_col
if(color > 0) baseprod_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) baseprod_line_bw
if(bw > 0) baseprod_fill_bw
```

Regional baseline production

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) baseprod_reg_line_col
if(color > 0) baseprod_reg_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) baseprod_reg_line_bw
if(bw > 0) baseprod_reg_fill_bw
```

## All Scenarios

Complete Set

```{r}
if(color > 0) gridmix_all_col
if(bw > 0) gridmix_all_bw
```

Parsed Set

```{r}
if(color > 0) gridmix_col
if(bw > 0) gridmix_bw
```

## Regional Mix

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0)gridmix_r1_col
if(color > 0)gridmix_r1_bar_col
if(color > 0)gridmix_r2_col
if(color > 0)gridmix_r2_bar_col
if(color > 0)gridmix_r3_col
if(color > 0)gridmix_r3_bar_col
if(color > 0)gridmix_r4_col
if(color > 0)gridmix_r4_bar_col
if(color > 0)gridmix_r5_col 
if(color > 0)gridmix_r5_bar_col
if(color > 0)gridmix_r6_col  
if(color > 0)gridmix_r6_bar_col
if(color > 0)gridmix_r7_col  
if(color > 0)gridmix_r7_bar_col
if(color > 0)gridmix_r8_col  
if(color > 0)gridmix_r8_bar_col
if(color > 0)gridmix_r9_col  
if(color > 0)gridmix_r9_bar_col
if(bw > 0)gridmix_r1_bw 
if(bw > 0)gridmix_r1_bar_bw 
if(bw > 0)gridmix_r2_bw 
if(bw > 0)gridmix_r2_bar_bw  
if(bw > 0)gridmix_r3_bw 
if(bw > 0)gridmix_r3_bar_bw 
if(bw > 0)gridmix_r4_bw 
if(bw > 0)gridmix_r4_bar_bw 
if(bw > 0)gridmix_r5_bw 
if(bw > 0)gridmix_r5_bar_bw 
if(bw > 0)gridmix_r6_bw 
if(bw > 0)gridmix_r6_bar_bw 
if(bw > 0)gridmix_r7_bw 
if(bw > 0)gridmix_r7_bar_bw 
if(bw > 0)gridmix_r8_bw 
if(bw > 0)gridmix_r8_bar_bw 
if(bw > 0)gridmix_r9_bw 
if(bw > 0)gridmix_r9_bar_bw 
```

## Emissions Cap

BAU emissions

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) bau_facetcost_line_col
if(color > 0) bau_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) bau_facetcost_line_bw
if(bw > 0) bau_facetcost_fill_bw
```

30% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em30_facetcost_line_col
if(color > 0) em30_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em30_facetcost_line_bw
if(bw > 0) em30_facetcost_fill_bw
```

40% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em40_facetcost_line_col
if(color > 0) em40_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em40_facetcost_line_bw
if(bw > 0) em40_facetcost_fill_bw
```

50% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em50_facetcost_line_col
if(color > 0) em50_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em50_facetcost_line_bw
if(bw > 0) em50_facetcost_fill_bw
```

60% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em60_facetcost_line_col
if(color > 0) em60_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em60_facetcost_line_bw
if(bw > 0) em60_facetcost_fill_bw
```

70% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em70_facetcost_line_col
if(color > 0) em70_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em70_facetcost_line_bw
if(bw > 0) em70_facetcost_fill_bw
```

80% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em80_facetcost_line_col
if(color > 0) em80_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em80_facetcost_line_bw
if(bw > 0) em80_facetcost_fill_bw
```

## Cost Reductions

50% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost50_facetem_line_col
if(color > 0) cost50_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost50_facetem_line_bw
if(bw > 0) cost50_facetem_fill_bw
```

60% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost60_facetem_line_col
if(color > 0) cost60_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost60_facetem_line_bw
if(bw > 0) cost60_facetem_fill_bw
```

70% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost70_facetem_line_col
if(color > 0) cost70_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost70_facetem_line_bw
if(bw > 0) cost70_facetem_fill_bw
```

80% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost80_facetem_line_col
if(color > 0) cost80_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost80_facetem_line_bw
if(bw > 0) cost80_facetem_fill_bw
```

## Heatmaps

```{r}
if(color > 0) heatmap_col
if(bw > 0) heatmap_bw
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) osw_grid_heatmap_col
if(color > 0) wnd_grid_heatmap_col
if(color > 0) sol_grid_heatmap_col
if(color > 0) coal_grid_heatmap_col
if(color > 0) nga_grid_heatmap_col
if(color > 0) nuk_grid_heatmap_col
if(color > 0) hyd_grid_heatmap_col
if(color > 0) ccs_grid_heatmap_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) osw_grid_heatmap_bw 
if(bw > 0) wnd_grid_heatmap_bw 
if(bw > 0) sol_grid_heatmap_bw 
if(bw > 0) coal_grid_heatmap_bw
if(bw > 0) nga_grid_heatmap_bw 
if(bw > 0) nuk_grid_heatmap_bw 
if(bw > 0) hyd_grid_heatmap_bw 
if(bw > 0) ccs_grid_heatmap_bw
```

## Market Share

```{r}
oswmarket %>% split(.$Technology) %>% map(summary)
marketShareTable
```

## Renewable Contributions

```{r}
if(color > 0) rps_col
if(bw > 0) rps_bw
```

## Retirements and Additions

Basecase year-on-year changes in the grid mix. Shows the modeled fluctuations in generation. All following quantifications of grid mix changes are as compared to these changes in the basecase.

```{r}
if(color > 0) base_retire_fill_col
if(bw > 0) base_retire_fill_bw
```

## Changes Over Baseline

Summary Graph 

```{r}
if (color > 0) prod_dif_all_col
if(bw > 0) prod_dif_all_bw
```
```{r}
if (color > 0) prod_dif_col
if(bw > 0) prod_dif_bw
```

Regional Summary Graphs

```{r}
if(color > 0) prod_dif_r1_col
if(color > 0) prod_dif_r2_col
if(color > 0) prod_dif_r3_col
if(color > 0) prod_dif_r4_col
if(color > 0) prod_dif_r5_col
if(color > 0) prod_dif_r6_col
if(color > 0) prod_dif_r7_col
if(color > 0) prod_dif_r8_col
if(color > 0) prod_dif_r9_col
if(bw > 0) prod_dif_r1_bw
if(bw > 0) prod_dif_r2_bw
if(bw > 0) prod_dif_r3_bw
if(bw > 0) prod_dif_r4_bw
if(bw > 0) prod_dif_r5_bw
if(bw > 0) prod_dif_r6_bw
if(bw > 0) prod_dif_r7_bw
if(bw > 0) prod_dif_r8_bw
if(bw > 0) prod_dif_r9_bw
```

By Emissions Reduction %

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) prod_dif_bau_col
if(color > 0) prod_dif_e30_col
if(color > 0) prod_dif_e40_col
if(color > 0) prod_dif_e50_col
if(color > 0) prod_dif_e60_col
if(color > 0) prod_dif_e70_col
if(color > 0) prod_dif_e80_col
if(bw > 0) prod_dif_bau_bw
if(bw > 0) prod_dif_e30_bw
if(bw > 0) prod_dif_e40_bw
if(bw > 0) prod_dif_e50_bw
if(bw > 0) prod_dif_e60_bw
if(bw > 0) prod_dif_e70_bw
if(bw > 0) prod_dif_e80_bw
```

By Cost Reduction %

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) prod_dif_c40_col
if(color > 0) prod_dif_c50_col
if(color > 0) prod_dif_c60_col
if(color > 0) prod_dif_c70_col
if(color > 0) prod_dif_c80_col
if(bw > 0) prod_dif_c40_bw
if(bw > 0) prod_dif_c50_bw
if(bw > 0) prod_dif_c60_bw
if(bw > 0) prod_dif_c70_bw
if(bw > 0) prod_dif_c80_bw
```

# Emissions

## Baseline

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) emis_bau_line_col
if(color > 0) emis_bau_fill_col
if(bw > 0) emis_bau_line_bw
if(bw > 0) emis_bau_fill_bw
```

## Emissions by Scenario and Commodity

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) emis_col
if(color > 0) emis_perc_col
if(bw > 0) emis_bw
if(bw > 0) emis_perc_bw
```

## Emissions by Commodity - Values

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) co2_col
if(color > 0) co2_hm_col
if(color > 0) so2_col
if(color > 0) so2_hm_col
if(color > 0) nox_col
if(color > 0) nox_hm_col
if(color > 0) ch4_col
if(color > 0) ch4_hm_col
if(color > 0) pm2.5_col
if(color > 0) pm2.5_hm_col
if(bw > 0) co2_bw
if(bw > 0) co2_hm_bw
if(bw > 0) so2_bw
if(bw > 0) so2_hm_bw
if(bw > 0) nox_bw
if(bw > 0) nox_hm_bw
if(bw > 0) ch4_bw
if(bw > 0) ch4_hm_bw
if(bw > 0) pm2.5_bw
if(bw > 0) pm2.5_hm_bw
```

## Emissions by Commodity - Percent Reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) co2_hm_per_col
if(color > 0) so2_hm_per_col
if(color > 0) nox_hm_per_col
if(color > 0) ch4_hm_per_col
if(color > 0) pm2.5_hm_per_col
if(bw > 0) co2_hm_per_bw
if(bw > 0) so2_hm_per_bw
if(bw > 0) nox_hm_per_bw
if(bw > 0) ch4_hm_per_bw
if(bw > 0) pm2.5_hm_per_bw
```


# Total Electricity Production

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) elctotal_line_col
if(color > 0) elctotal_heat_col
if(bw > 0) elctotal_line_bw
if(bw > 0) elctotal_heat_bw
```


# Correlations

```{r}
chart.Correlation(oswcor, histogram = FALSE, method = "spearman")
```

# Regressions

```{r, results = 'asis'}
grid.modeltable
emission.modeltable
```































