---
title: "Offshore Wind Results and Analysis"
author: "Morgan Browning"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    number_sections: yes
    toc: yes
---

***

# Disclosure

This document functions as an all-inclusive working directory for synthesis and graphical analysis of the results from the offshore wind research of Morgan Browning, an ORISE Fellow at the U.S. Environmental Protection Agency's Office of Research and Development. This document and its contents are not finalized nor are intended for publication. 

It is annotated primarily for ease of reproducability and a general understanding of the results. Graphs are provided with many variations to meet criteria of different publication and presentation platforms.

# Setup

Three scripts are loaded into this markdown document to allow for analysis of the data. The setup script loads the library, creates generalized functions, and creates global variables for color scales and factors. The data script loads the excel spreadsheet with all of the results data and performs the majority of data munging. The results script creates charts, graphs, and tables. This report functions as the annotated synthesis of the data and results.

```{r setup, include = FALSE}
# Sets global knit options and loads the setup and data import scripts for the project. Code is hidden for ease of reading. Was running into issues when cacheing results, so have set cache to false. Time to knit <5 minutes, so it does not cause much of an issue. Will consider cacheing in the future if the issue is resolved.
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE, tidy = TRUE, cache = FALSE)
```
```{r}
source("osw_Scripts/osw_setup.R")
source("osw_Scripts/osw_data.R")
source("osw_Scripts/osw_results.R")
```
```{r colorcalls}
# Creates toggles for selecting the color scale of graphics to be printed [color, black & white, gray]. More than one may be selected.
color <- 1
bw <- 1
gray <- 1
```

# Scenarios

The nested parametric sensitivity analysis was built on combinations of two sets of scenarios:

1. Electric sector CO~2~ emissions caps, as a linear decrease to a given % decrease from 2010 emissions by 2050

2. Cost reductions of offshore wind, as a linear decrease to a given % decrease from 2010 costs by 2035, then level costs to 2050

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost_col
if(color > 0) emissions_col
```

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost_bw
if(bw > 0) emissions_bw
```

# LCOE

EIA's AEO 2019 provides the following values for the estimated levelized cost of electricity (capacity-weighted average) for new generation resources entering service in 2023 (2018 $/MWh). Offshore wind has the highest total LCOE by a large margin. The second most expensive technology is biomass. The AEO LCOE was used in the calculation of offshore wind costs for the above cost curves, but LCOE is not directly used in the model.

```{r}
lcoe_table
```

# Offshore Wind

As offshore wind is the primary technology being assessed in this research, we have explored many facets of offshore wind buildout. These facets are explored below, both at a regional and national cumulative level.

## Capacity Buildout

Cumulative and new addition offshore wind capacity across all nine census regions, by cost and emissions reduction scenario.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cap_col_side
if(color > 0) newcap_col_top
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cap_bw_side
if(bw > 0) newcap_bw_top
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(gray > 0) cap_gray_side
if(gray > 0) newcap_gray_top
```

## Total Capacity

Total offshore wind capacity across all nine census regions in 2050, by cost and emissions reduction scenario.

```{r}
if(color > 0) cap_col_heat 
if(bw > 0) cap_bw_heat
```
```{r}
cap_2050_table
```

## Output

Total offshore wind electricity output across all nine census regions, by cost and emissions reduction scenario.

```{r}
if(color > 0) output_col_side
if(bw > 0) output_bw_side
if(gray > 0) output_gray_side
```
```{r}
output_2050_table 
```

## Regions

Cumulative and new addition offshore wind capacity by region.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cap_reg1_col
if(color > 0) newcap_reg1_col
if(color > 0) cap_reg2_col
if(color > 0) newcap_reg2_col
if(color > 0) cap_reg3_col
if(color > 0) newcap_reg3_col
if(color > 0) cap_reg4_col
if(color > 0) newcap_reg4_col
if(color > 0) cap_reg5_col
if(color > 0) newcap_reg5_col
if(color > 0) cap_reg6_col
if(color > 0) newcap_reg6_col
if(color > 0) cap_reg7_col
if(color > 0) newcap_reg7_col
if(color > 0) cap_reg9_col
if(color > 0) newcap_reg9_col
```

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cap_reg1_bw
if(bw > 0) newcap_reg1_bw
if(bw > 0) cap_reg2_bw
if(bw > 0) newcap_reg2_bw
if(bw > 0) cap_reg3_bw
if(bw > 0) newcap_reg3_bw
if(bw > 0) cap_reg4_bw
if(bw > 0) newcap_reg4_bw
if(bw > 0) cap_reg5_bw
if(bw > 0) newcap_reg5_bw
if(bw > 0) cap_reg6_bw
if(bw > 0) newcap_reg6_bw
if(bw > 0) cap_reg7_bw
if(bw > 0) newcap_reg7_bw
if(bw > 0) cap_reg9_bw
if(bw > 0) newcap_reg9_bw
```

Cumulative and new addition offshore wind capacity by region, emissions reduction, and cost reduction.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cap_allreg_col
if(color > 0) newcap_allreg_col
if(color > 0) cap_allreg_col_free
if(color > 0) newcap_allreg_col_free
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cap_allreg_bw
if(bw > 0) newcap_allreg_bw
if(bw > 0) cap_allreg_bw_free
if(bw > 0) newcap_allreg_bw_free
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
cap_region_table
output_region_table
```

# Grid Mix

## Baseline Production

Grid mix without any offshore wind cost reduction or emissions cap.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) baseprod_line_col
if(color > 0) baseprod_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) baseprod_line_bw
if(bw > 0) baseprod_fill_bw
```

## All Scenarios

Complete Set

```{r}
if(color > 0) gridmix_all_col
if(bw > 0) gridmix_all_bw
```

Parsed Set

```{r}
if(color > 0) gridmix_col
if(bw > 0) gridmix_bw
```

## Emissions Cap

BAU emissions

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) bau_facetcost_line_col
if(color > 0) bau_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) bau_facetcost_line_bw
if(bw > 0) bau_facetcost_fill_bw
```

30% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em30_facetcost_line_col
if(color > 0) em30_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em30_facetcost_line_bw
if(bw > 0) em30_facetcost_fill_bw
```

40% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em40_facetcost_line_col
if(color > 0) em40_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em40_facetcost_line_bw
if(bw > 0) em40_facetcost_fill_bw
```

50% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em50_facetcost_line_col
if(color > 0) em50_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em50_facetcost_line_bw
if(bw > 0) em50_facetcost_fill_bw
```

60% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em60_facetcost_line_col
if(color > 0) em60_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em60_facetcost_line_bw
if(bw > 0) em60_facetcost_fill_bw
```

70% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em70_facetcost_line_col
if(color > 0) em70_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em70_facetcost_line_bw
if(bw > 0) em70_facetcost_fill_bw
```

80% emissions reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) em80_facetcost_line_col
if(color > 0) em80_facetcost_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) em80_facetcost_line_bw
if(bw > 0) em80_facetcost_fill_bw
```

## Cost Reductions

40% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost40_facetem_line_col
if(color > 0) cost40_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost40_facetem_line_bw
if(bw > 0) cost40_facetem_fill_bw
```

50% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost50_facetem_line_col
if(color > 0) cost50_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost50_facetem_line_bw
if(bw > 0) cost50_facetem_fill_bw
```

60% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost60_facetem_line_col
if(color > 0) cost60_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost60_facetem_line_bw
if(bw > 0) cost60_facetem_fill_bw
```

70% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost70_facetem_line_col
if(color > 0) cost70_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost70_facetem_line_bw
if(bw > 0) cost70_facetem_fill_bw
```

80% cost reduction

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) cost80_facetem_line_col
if(color > 0) cost80_facetem_fill_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) cost80_facetem_line_bw
if(bw > 0) cost80_facetem_fill_bw
```

## Heatmaps

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) osw_grid_heatmap_col
if(color > 0) wnd_grid_heatmap_col
if(color > 0) sol_grid_heatmap_col
if(color > 0) coal_grid_heatmap_col
if(color > 0) nga_grid_heatmap_col
if(color > 0) nuk_grid_heatmap_col
if(color > 0) hyd_grid_heatmap_col
if(color > 0) ccs_grid_heatmap_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(bw > 0) osw_grid_heatmap_bw 
if(bw > 0) wnd_grid_heatmap_bw 
if(bw > 0) sol_grid_heatmap_bw 
if(bw > 0) coal_grid_heatmap_bw
if(bw > 0) nga_grid_heatmap_bw 
if(bw > 0) nuk_grid_heatmap_bw 
if(bw > 0) hyd_grid_heatmap_bw 
if(bw > 0) ccs_grid_heatmap_bw
```

## Retirements and Additions

```{r, out.width=c('50%', '50%'), fig.show='hold'}
if(color > 0) base_retire_fill_col
if(bw > 0) base_retire_fill_bw
```

## Grid Mix Changes Over Baseline

```{r, out.width=c('50%', '50%'), fig.show='hold'}

```
```{r, out.width=c('50%', '50%'), fig.show='hold'}

```

# TEST

```{r}
grid.arrange(cost_col, cost_bw, emissions_col, emissions_bw, layout_matrix = rbind(c(1,1,1),c(2,3,4)))
grid.arrange(cost_col, cost_bw, emissions_col, emissions_bw, ncol = 2)
```

