---
title: "Modeling the Contribution of Offshore Wind to the Grid Mix and Air Quality Implications:\nNational Approach Results and Analysis"
author: "Morgan Browning"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    number_sections: yes
    toc: yes
header-includes:
  - \usepackage[labelformat=empty]{caption}
editor_options: 
  chunk_output_type: console
---

***

```{r setup, include = FALSE}
# Sets global knit options and loads the setup and data import scripts for the project. Code is hidden for ease of reading. Was running into issues when cacheing results, so have set cache to false. Time to knit <5 minutes, so it does not cause much of an issue. Will consider cacheing in the future if the issue is resolved.
knitr::opts_chunk$set(echo = FALSE, include = TRUE, warning = FALSE, message = FALSE, tidy = TRUE, cache = FALSE)
```
```{r, include = FALSE}
source("osw_Scripts/osw_setup.R")
```
```{r, include = FALSE}
source("osw_Scripts/osw_data.R")
```
```{r, include = FALSE}
source("osw_Scripts/osw_results.R")
```


# Scenarios

The nested parametric sensitivity analysis was built on combinations of two sets of scenarios:

1. Electric sector CO~2~ emissions caps, as a linear decrease to a given % decrease from 2010 emissions by 2050  
  + Business and usual emissions represent approximately a 20% reduction in CO~2~ emissions

2. Cost reductions of offshore wind, as a linear decrease to a given % decrease from 2010 costs by 2035, then level costs to 2050  
  + A 20% cost reduction is used as the base case, assuming very conservative technological advancement and little benefit of economies of scale
  + Cost curves are set to resolve by 2035 as estimated based on NREL LCOE cost projections for offshore wind

```{r, out.width=c('50%', '50%'), fig.show='hold'}
emissionsscen_col
costscen_col
```

# LCOE

EIA's AEO 2019 provides the following values for the estimated levelized cost of electricity (capacity-weighted average) for new generation resources entering service in 2023 (2018 $/MWh). Offshore wind has the highest total LCOE by a large margin. The second most expensive technology is biomass. The AEO LCOE was used in the calculation of offshore wind costs for the above cost curves, but LCOE is not directly used in the model.

```{r}
lcoe_table
```

# Offshore Wind

As offshore wind is the primary technology being assessed in this research, we have explored many facets of offshore wind buildout. These facets are explored below, both at a regional and national cumulative level.

## Capacity Buildout

Cumulative and new addition offshore wind capacity across all nine census regions, by cost and emissions reduction scenario.

```{r, out.width=c('50%', '50%'), fig.show='hold'}
cap_col_side
newcap_col_top
```

## Total Capacity

Total offshore wind capacity across all nine census regions in 2050, by cost and emissions reduction scenario.

```{r}
cap_col_heat 
cap_2050_table
```

## Regions

Cumulative and new addition offshore wind capacity by region, emissions reduction, and cost reduction.

```{r}
cap_region_table
regOSW_map_col
```

# Grid Mix

## Baseline Production

Grid mix without any offshore wind cost reduction or emissions cap.

```{r}
baseprod_line_col
baseprod_fill_col
```

## All Scenarios

Complete Set

```{r}
gridmix_all_col
```

Parsed Set

```{r}
gridmix_col
```

## Heatmaps

```{r}
heatmap_col
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
osw_grid_heatmap_col
wnd_grid_heatmap_col
sol_grid_heatmap_col
coal_grid_heatmap_col
nga_grid_heatmap_col
nuk_grid_heatmap_col
hyd_grid_heatmap_col
ccs_grid_heatmap_col
other_grid_heatmap_col
```

## Market Share

```{r}
marketShareTable
marketshare_heatmap
```

## Renewable Contributions

```{r}
rps_col
```

## Retirements and Additions

Summary Graph 

```{r}
prod_dif_col
```

# Emissions

## Emissions by Scenario and Commodity

```{r, out.width=c('50%', '50%'), fig.show='hold'}
emis_col
emis_perc_col
```

## Emissions by Commodity - Percent Reduction

```{r}
emis_perc_hm
```
```{r, out.width=c('50%', '50%'), fig.show='hold'}
co2_hm_per_col
so2_hm_per_col
nox_hm_per_col
ch4_hm_per_col
pm2.5_hm_per_col
```

# Total Electricity Production

```{r, out.width=c('50%', '50%'), fig.show='hold'}
elctotal_line_col
elctotal_heat_col
```

# End Use ELC

```{r}
sector_line
sector_split_ind
ind_split_line
```

# Correlations

```{r}
chart.Correlation(oswcor, histogram = TRUE, method = "spearman")
```

# Regressions

## Full set of models

OSW Capacity, % Renewables, and Total Elc Production Regressions

```{r, results = 'asis'}
grid_modeltable
grid_graph
```

Emissions Regressions

```{r, results = 'asis'}
emission_modeltable
emission_graph
```

## Emission-specific regressions by CO2 cap scenario

CO2

```{r, results = 'asis'}
co2_modeltable
co2_graph
```

SO2

```{r, results = 'asis'}
so2_modeltable
so2_graph
```

NOx

```{r, results = 'asis'}
nox_modeltable
nox_graph
```

PM 2.5

```{r, results = 'asis'}
pm2.5_modeltable
pm2.5_graph
```

CH4

```{r, results = 'asis'}
ch4_modeltable
ch4_graph
```

## CO2 cap regressions by emissions type

```{r,results = 'asis'}
emission_fullmodeltable
```

BAU

```{r, results = 'asis'}
bau_modeltable
bau_graph
```

30% CO2 Cap

```{r, results = 'asis'}
e30_modeltable
e30_graph
```

40% CO2 Cap

```{r, results = 'asis'}
e40_modeltable
e40_graph
```

50% CO2 Cap

```{r, results = 'asis'}
e50_modeltable
e50_graph
```

60% CO2 Cap

```{r, results = 'asis'}
e60_modeltable
e60_graph
```

70% CO2 Cap

```{r, results = 'asis'}
e70_modeltable
e70_graph
```

80% CO2 Cap

```{r, results = 'asis'}
e80_modeltable
e80_graph
```

